---
title: "Tidyverse"
---

## Introduction

The goal of the package is to detail a package in Tidyverse. We will discuss forcats/dplyr. Dplyr is much more versatile by nature. We will also take a look at the purr package.   

```{r, load-data, message=FALSE, echo=TRUE}
women <- read.csv("https://raw.githubusercontent.com/gc521/DATA-607-Tidyverse/main/women-stem.csv")
install.packages("tidyverse")
library(tidyverse)
install.packages('DT')
library(DT)
```
Fac_infreq function can be called to quickly order factor variable by appearance/level of frequency. This makes the appearance of tables/graphs more apparent. We also make use of the DPLYR to create a count of the major_category variable. 

```{r, fct}
women$Major_category <- as.factor(women$Major_category)
women$Major_category <- fct_infreq(women$Major_category)
summary(women$Major_category)


Major_category <- as.data.frame(summary(women$Major_category))

datatable(Major_category, colnames = c("Count"))

women <- women |> group_by(Major_category) |> mutate(Count = n())


p <-ggplot(women, aes(x=Major_category, fill = Major_category)) + geom_bar() + theme_dark() + coord_flip() + geom_text(aes(y=1, label = Count), hjust = -2.0, color = 'white')







```

