---
title: "tidyverse"
author: "Susanna Wong"
date: "2023-04-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load data

The data is in store in a csv file that can be found here.

Use `read.csv` from `readr` package to read the csv file as a dataframe.
Use `<-` to store the data as a variable in R.
Below, we store the data as `raw_data`.
You can use `glimpse()` from `dplyr` package to get a glimpse of the data.

```{r, message=FALSE}
raw_data <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/recent-grads.csv")
library(DT)
datatable(raw_data, options = list(scrollX = TRUE))
```

# Which major category has the highest share of women? {.tabset}

## Analysis

In the `raw_data`, there are detailed information for each of the 173 majors.
In order to answer the question, we need to group the major category, and find the total people, total women, and total men for each major category.

It seems that the `raw_data` is already tidied.
We should create a new dataframe for our analysis and make no changes to the `raw_data`.

Use `%>%` from the `magrittr` package to pipe the `raw_data` into our new dataframe, `college_major`.

    college_major <- raw_data %>%

Next, use `group_by()` function from the `dplyr` package to group rows by column value, `Major_category`.

    college_major <- raw_data %>%
      group_by(Major_category) %>%
o
```{r pressure, echo=FALSE}
library(dplyr)
library(DT)

college_major <- raw_data %>%
  group_by(Major_category) %>%
  summarise(Total = sum(Total,na.rm=TRUE), Men = sum(Men,na.rm=TRUE), Women = sum(Women,na.rm=TRUE)) %>%
  mutate(ShareWomen = Women/Total)

datatable(college_major)
```

# Including Plots

```{r}
# install.packages('ggplot2')
library(ggplot2)

ggplot(data = college_major, aes(x = reorder(Major_category, ShareWomen), y = ShareWomen)) + geom_bar(stat="identity") + coord_flip() 
```

# Source

Below are links to get more information related to the functions in the mentioned packages. 

<https://www.tidyverse.org/packages/>

https://readr.tidyverse.org/

<https://dplyr.tidyverse.org/reference/index.html>

<https://ggplot2.tidyverse.org/reference/>

https://rstudio.github.io/DT/

